Make any stupid plot you want

### 2020-09-24 draft/intro.tex
start

\section{Notation \& Definitions}

@@

\subsection{Grammar of Graphics \& ggplot}
Specifies the end chart (graphic)
we want to specify the transformations ....
\begin{figure}
    \includegraphics{figures/intro/grammar_chart_composition.png}
    \caption{page 10 (introduction)}
\end{figure}
\begin{figure}
    \includegraphics{figures/intro/grammar_example.png}
    \caption{Wilkenson decomposed a graphic into ...} 
\end{figure}
\cite{wilkinsonGrammarGraphicsStatistics2005}
charts - words 
    - instances of much more general objects (geometric primatives)
    - histogram =/= bar chart
graphics - statements 
expliceltly OO
    1. specification
        data - operations/computations
        trans - variable transforms (rank)
        scale - scale transforms
        coord - coordinate system
        element - marks and channels
        guide - meta elements - (axes, legends, etc)
    2. assembly - kinda what happens in artist (spec->something that can go to renderer) 
    3. display - rendering

>>>>

\section{Notation \& Definitions}
System of transforms:
input: data w/ structure on fiber bundle + measurement type
artist: data -> visualization
(what structure of input is preserved in output)
we can provide list of
artist : topology it preserves
point/line/face parameters: measurement type properties

ex: 
Line2D preserves continuity
Linestyle: categorical

%%define basic properties of measurement of types in a theoretical way or C&P from a paper

Miniumum assumption a transform will make - is this a valid transform for the slot?

Set of questions/rules to apply such that see a new artist can be defined which lets us maybe simplify optimizations.

M, Fiber Bundle, Section, operatons on \{data, visual\}, transform data space \& visual space,

topology gives us that m is preserved
spivak gives us that v is preserved

temperature on globe:
\begin{equation}
data = [[t1], [t2_{la1, lo2}]
fiber = {lat, lon, temp}
m = the data is 2d continous
\end{equation}
artist has implict m
aesthetic paremeters transform in fiber that preserves type operations \& relations in the fiber
lat - relative distance + ordering

\subsubsection{Graphical Elements}
There is a set of transform functions $T$ that maps from the data space $D$ to the visual space composed of geometric marks and aesthetic channels $V$ \cite{bertinIIPropertiesGraphic2011, munznerMarksChannels}.  We propose that a visualization is 
\begin{equation}
    T: D \rightarrow V
\end{equation}

Wilkenson proposes  that visualization is  \cite{wilkinsonGrammarGraphics2005, wilkinsonMathematicalFoundationAnalytic2010}

\begin{align}
\label{eq:gog_data_range}
G &= {(x, f(x)): x \in R and f(x)=e^{-x^2}}\\
F &= [-3,3] x [0,1]
\end{align}

\begin{equation}
\label{eq:gog_aesthetic_mapping}
A: x \mapsto x_{position}, f(x) \mapsto y_{position}
\end{equation}

\begin{equation}
G_{A} = A(F \cap G) 
\end{equation}

\subsection{What is the artist}
\begin{equation}
A: D \mapsto CW\\
\end{equation}

An artist is a function F from X to Y
that satisfyies properties P1, ... PN
Step 1: Define X
step 2: Define Y
Spefiy Pi in terms of equations.

@@

\subsection{Grammar of Graphics \& ggplot}
Specifies the end chart (graphic)
we want to specify the transformations ....
\begin{figure}
    \includegraphics{figures/intro/grammar_chart_composition.png}
    \caption{page 10 (introduction)}
\end{figure}

\begin{figure}
    \includegraphics{figures/intro/grammar_example.png}
    \caption{Wilkenson decomposed a graphic into ...} 
\end{figure}

charts - words 
    - instances of much more general objects (geometric primatives)
    - histogram =/= bar chart
graphics - statements 
expliceltly OO
    1. specification
        data - operations/computations
        trans - variable transforms (rank)
        scale - scale transforms
        coord - coordinate system
        element - marks and channels
        guide - meta elements - (axes, legends, etc)
    2. assembly - kinda what happens in artist (spec->something that can go to renderer) 
    3. display - rendering
